SummaryStats

### 2023-03-02 analysis/code/SubExperiments.Rmd
#1 working version of GenSubExps

build %>% 
  semi_join(d_cities, by="city_id") %>% 
  filter(year %in% inclusion_range) %>% 
  group_by(city_id) %>% 
  filter(n() == 3*W+1) %>% 
  ggplot()+
  geom_bar(aes(x=year))

>>>>

build %>% 
  semi_join(d_cities, by="city_id") %>% 
  filter(year %in% inclusion_range) %>% 
  group_by(city_id) %>% 
  filter(n() == 3*W+1) %>% 
  summarise() # %>% 
  # ggplot()+
  # geom_bar(aes(x=year))
